Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-07 paper_jasa.tex
subject specific power curves added again

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.45}{\includegraphics{effect_power_subject_exp1.pdf}}
       \scalebox{0.45}{\includegraphics{effect_power_subject_exp2.pdf}}
       \caption{Subject specific power obtained from Equation \ref{eqn:effect} and the power of UMP test for different effect size $E$ as per experiment 1 and 2.}
       \label{fig:power_effect_subject1}
\end{figure*}

@@

@@

\subsection{Estimating $p$-value in on-Classical Settings}

>>>>

@@

%\begin{figure*}[hbtp]
%   \centering
%       \scalebox{0.45}{\includegraphics{effect_power_subject_exp1.pdf}}
%       \scalebox{0.45}{\includegraphics{effect_power_subject_exp2.pdf}}
%       \caption{Subject specific power obtained from Equation \ref{eqn:effect} and the power of UMP test for different effect size $E$ as per experiment 1 and 2.}
%       \label{fig:power_effect_subject1}
%\end{figure*}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{power_screening_subject.pdf}}
      \caption{The subject specific power estimated from model \ref{mixed} are shown for various data sets obtained by applying 5 screening criteria.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown in pink lines for comparison.}
       \label{fig:power_screening_subject}	
\end{figure}

\subsection{Estimating $p$-value in Non-Classical Settings}
